An Open Repository of Real-Time COVID-19 Indicators

### 2021-10-04 indicators/code/indicator-paper-figures.Rmd
Switch to DV-CLI instead of CHNG-CLI
Historical CHNG data is currently suspect due to an issue in
reconstructing issue dates of the CHNG signals; rather than relying on
CHNG data here, we use DV-CLI, which gives similar results with less
concern about incorrect issue date information.

```{r figure-6-data, message=FALSE, cache=TRUE}
SOURCES <- c("chng", "fb-survey", "jhu-csse", "jhu-csse")
SIGNALS <- c("smoothed_outpatient_cli", "smoothed_whh_cmnty_cli",
             "confirmed_incidence_prop", "deaths_incidence_prop")
NAMES <- c("lag", "CHNG-CLI", "CTIS-CLI-in-community", "Cases", "Deaths")

>>>>

```{r figure-6-data, message=FALSE, cache=TRUE}
SOURCES <- c("doctor-visits", "fb-survey", "jhu-csse", "jhu-csse")
SIGNALS <- c("smoothed_cli", "smoothed_whh_cmnty_cli",
             "confirmed_incidence_prop", "deaths_incidence_prop")
NAMES <- c("lag", "DV-CLI", "CTIS-CLI-in-community", "Cases", "Deaths")

### 2021-10-04 indicators/paper/paper.tex
Switch to DV-CLI instead of CHNG-CLI
Historical CHNG data is currently suspect due to an issue in
reconstructing issue dates of the CHNG signals; rather than relying on
CHNG data here, we use DV-CLI, which gives similar results with less
concern about incorrect issue date information.

The revision tracking feature in the API assists in model-building and
evaluation. Figure~\ref{fig:dv_as_of} illustrates how one COVIDcast medical
claims signal evolved as it was revised across multiple issue dates, in four
different states, between June 1 and August 1, 2020. In each plot, the rightmost
ends of the lines correspond to estimates for the last day that data are
available for each issue date, which are generally the most tentative estimates,
and appear to be significantly biased upward in Arizona in June 2020, and
significantly biased downward in New York throughout June and July 2020.

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/dv_as_of.pdf}
  \caption{Estimated percentage of doctor's visits due to COVID-like illness
    displayed across multiple issue dates, with later issue dates adding
    additional data and revising past data from prior issue dates.}
  \label{fig:dv_as_of}
\end{figure}

>>>>

The revision tracking feature in the API assists in model-building and
evaluation. Figure~\ref{fig:dv_as_of} illustrates how one COVIDcast medical
claims signal evolved as it was revised across multiple issue dates, in four
different states, between June 1 and August 1, 2020. This signal, known as
DV-CLI, is similar to CHNG-CLI and measures outpatient doctor visits about
COVID-related symptoms, but is provided by a different data partner. In each
plot, the rightmost ends of the lines correspond to estimates for the last day
that data are available for each issue date, which are generally the most
tentative estimates, and appear to be significantly biased upward in Arizona in
June 2020, and significantly biased downward in New York throughout June and
July 2020.

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{fig/dv_as_of.pdf}
  \caption{Estimated percentage of doctor's visits due to COVID-like illness
    (DV-CLI) displayed across multiple issue dates, with later issue dates
    adding additional data and revising past data from prior issue dates.}
  \label{fig:dv_as_of}
\end{figure}
